Rising from the Ashes II: The Bar-driven Abundance Bimodality of the Milky Way

### 2025-02-18 paper/ms.tex
Small adjustment for appendix

We show the abundance distributions of 16 random subhalos from our $z=1.5$ catalog, and the subhalo we selected, in Appendix~\ref{app:rand_fig1}. Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way. After the $\alpha$-enhancement, a few have strongly bimodal features: 172175, 178140, 193025. It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}. Furthermore, if a galaxy had \alphaFe{} slowly and continuously decrease with time, then our $\alpha$-enhancement would not give rise to a bimodality since it is also a continuous adjustment.

>>>>

We show the abundance distributions of 16 random subhalos from our \edit1{Milky Way-progenitor mass} catalog, and the subhalo we selected, \edit1{at $z=0$} in Appendix~\ref{app:rand_fig1}. Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way. \edit1{After the $\alpha$-enhancement, six of the additional galaxies shown seem to have bimodal features: 143882, 167392, 348901, 425719, 439099, and 465255. However, none are as prominent as the fiducial galaxy (392276).} It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}. Furthermore, if a galaxy had \alphaFe{} slowly and continuously decrease with time, then our $\alpha$-enhancement would not give rise to a bimodality since it is also a continuous adjustment. \edit1{Appendix~\ref{app:rand_fig1} also shows the effect of choosing a different redshift at which to apply the enhancement ($z=1$, 1.5, and 2), which does not qualitatively change the bimodal structure in our fiducial galaxy.}
